RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2014-07-31 manuscripts/manuscript.Rmd
fix figure caption

```{r caption="Stochastic character mapping on a phylogeny, as generated by the phytools package after parsing the simmap-extended NeXML"}
library("phytools")
plotSimmap(phy)
```

>>>>

```{r Figure1, fig.cap="Stochastic character mapping on a phylogeny, as generated by the phytools package after parsing the simmap-extended NeXML."}
library("phytools")
plotSimmap(phy)
```
